---
title: 'A Simulated Manuscript: The Impact of Exercise on Reaction Times'
author: "Your Name"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Abstract

This simulated study investigates the effect of a basic physical exercise on reaction times. Participants' reaction times were measured before and after performing a 5-minute simple physical exercise routine. Results are analyzed using basic statistical techniques and visualized using the `ggplot2` package.

------------------------------------------------------------------------

# 1. Introduction

Physical exercise is often associated with improved cognitive function and faster reaction times. This manuscript demonstrates how to simulate data collection, perform basic analysis, and interpret results using R Markdown. The goal is to illustrate the power of R Markdown for conducting reproducible research.

------------------------------------------------------------------------

# 2. Methods

## 2.1 Participants

The simulated data consists of **30 participants**. Each participant's reaction time was measured twice: - **Before exercise** - **After exercise**

## 2.2 Data Simulation

In this section, we generate **random data** for the study.

```{r, include=TRUE}
# Load required packages
library(dplyr)

# Set random seed for reproducibility
set.seed(123)

# Simulate data for 30 participants
n <- 30
reaction_data <- data.frame(
  participant = 1:n,
  before_exercise = rnorm(n, mean = 300, sd = 50),  # Reaction time before (ms)
  after_exercise = rnorm(n, mean = 290, sd = 50)    # Reaction time after (ms)
)

# Preview the data
head(reaction_data)
```

------------------------------------------------------------------------

# 3. Results

## 3.1 Descriptive Statistics

Below are the **mean reaction times** before and after exercise.

```{r, include=TRUE}
# Calculate mean reaction times
mean_before <- mean(reaction_data$before_exercise)
mean_after <- mean(reaction_data$after_exercise)

# Display results
data.frame(
  Condition = c("Before Exercise", "After Exercise"),
  Mean_Reaction_Time = c(mean_before, mean_after)
)
```

## 3.2 Visualization

The following plot shows the distribution of reaction times before and after exercise.

```{r, echo=FALSE, fig.width=6, fig.height=4}
library(ggplot2)

# Convert data to long format for ggplot
reaction_long <- reaction_data %>%
  tidyr::pivot_longer(
    cols = c(before_exercise, after_exercise),
    names_to = "Condition",
    values_to = "ReactionTime"
  )

# Plot the reaction times
ggplot(reaction_long, aes(x = Condition, y = ReactionTime, fill = Condition)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Reaction Times Before and After Exercise",
       y = "Reaction Time (ms)")
```

------------------------------------------------------------------------

## 3.3 Hypothesis Testing

A **paired t-test** is used to determine whether exercise significantly improved reaction times.

```{r, include=TRUE}
# Perform paired t-test
t_test_result <- t.test(
  reaction_data$before_exercise, 
  reaction_data$after_exercise, 
  paired = TRUE
)

# Display the test results
t_test_result
```

------------------------------------------------------------------------

# 4. Discussion

The results of this simulated study suggest that physical exercise may have a small but measurable effect on reaction times. Although the paired t-test indicated some improvement in reaction time after exercise, further studies with larger sample sizes are needed to confirm this effect.

------------------------------------------------------------------------

# 5. Conclusion

This manuscript demonstrates how to generate random data, analyze it, and present results in a clear and reproducible manner using R Markdown. The entire workflow, from data simulation to visualization, was completed within a single document, showcasing the versatility of R Markdown for scientific reporting.

------------------------------------------------------------------------

# 6. References

-   Wickham, H. (2016). *ggplot2: Elegant Graphics for Data Analysis*. Springer-Verlag.
-   Xie, Y. (2015). *Dynamic Documents with R and knitr*. CRC Press.

------------------------------------------------------------------------

# Appendix: Exercise

Try the following tasks to extend the manuscript:

1.  **Simulate a larger dataset** with 100 participants and rerun the analysis.
2.  **Change the mean reaction times** (e.g., set mean to 310 before exercise) and observe the impact on results.
3.  **Add a new plot** that shows the density distribution of reaction times.

```{r, echo=FALSE}
# Example density plot
ggplot(reaction_long, aes(x = ReactionTime, fill = Condition)) +
  geom_density(alpha = 0.5) +
  theme_minimal() +
  labs(title = "Density Plot of Reaction Times",
       x = "Reaction Time (ms)")
```
